Interactive Checks for Coordination Avoidance

### 2019-08-16 doc/vldb_slides/sections/four_wise_men.tex
More speaker notes.

  \note{%
    Thankfully, Peter Bailis comes to save the day and reminds us that perhaps
    we can have the best of both worlds. In 2014, Peter and some other smart
    folks defined invariant confluence as a condition under which we can
    replicate a piece of data without the need for strongly consistent
    coordination while maintaining the data's application invariants.

>>>>

  \note{%
    Thankfully, Peter Bailis comes to save the day and reminds us that perhaps
    we can have the best of both worlds. In 2014, Peter and some other smart
    folks including Alan defined invariant confluence as a condition under
    which we can replicate a piece of data without the need for strongly
    consistent coordination while maintaining the data's application
    invariants.
